Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-26 demystify.tex
updates

For stipend, unlikely for TA, which is set by the university. Moreover, while RA is set by the adviser, it is often based on the department's standard, and it also would be unfair to other students if you get more.  However, your stipend is often increased every year (automatically by a small amount) and also after you pass your qualifier exams.

For start date or TA assignment (e.g., TA'ing a specific course), it is uncommon, but you can ask for it. Also, there is typically no moving allowance for PhD students. In short, standard things set by the university or department are unlikely non-negotiable.  However, you can ask for things such as computer equipment (\autoref{sec:buying-equipment}), books, (and sometimes even furniture), and a conference travel budget.

\section{Will I be miserable during my a PhD?}\label{sec:happy}
There are many stories of how students are mistreated, stressed, and miserable. Issues including bad relationships with professors, conflicts with co-authors and lab mates, feeling discriminated against (e.g., because you're an international student), \emph{do} exist, and it is good to be aware of those.  However, in reality, there are many good mentors, supportive lab mates and departments, and so on.  So don't let social media make you feel pessimistic and deter your quest to advance knowledge.

>>>>

It is unlike that you can negotiate TA stipend, which is set by the university. Moreover, while RA is set by the adviser, it is often based on the department's standard, and it also would be unfair to other students if you get more (especially since you're new and have not proven yourself yet). However, your stipend is often increased every year by the university (automatically by a small amount).

For start date or TA assignment (e.g., TA'ing a specific course), you can ask for it. Also, there is typically no moving allowance for PhD students. In short, standard things set by the university or department are unlikely non-negotiable.  However, you can ask for things such as computer equipment (\autoref{sec:buying-equipment}), books, (and maybe even furniture), and a conference travel budget.

% \section{Will I be miserable during my a PhD?}\label{sec:happy}
% There are many stories of how students are mistreated, stressed, and miserable. Issues including bad relationships with professors, conflicts with co-authors and lab mates, feeling discriminated against (e.g., because you're an international student), \emph{do} exist, and it is good to be aware of those.  However, in reality, there are many good mentors, supportive lab mates and departments, and so on.  So don't let social media make you feel pessimistic and deter your quest to advance knowledge.
